Parameterized convection, grid-scale clouds and resolution sensitivity in the Community Atmosphere Model

### 2019-08-16 resolution.tex
edits

\subsection{Biases Unaffected by Resolution}

Poleward of the deep tropics and within the subtropics, the logistic regression indicates that subsidence is a poor predictor of $FREQZM$ (Figure~\ref{fig:4zonal}a,b). The R-value decreases to a local minimum between $15^{\circ} - 20^{\circ}$ latitude, and the magnitude of the sensitivity parameter steeply declines. The local minimum in the R-value corresponds with a local maximum in the latent heat fluxes (Figure~\ref{fig:4zonal}c), indicating that the boundary layer is being driven unstable by large surface latent heat fluxes. The CAPE values in the $10^{\circ} - 15^{\circ}$ latitude region are likely to be small, since the ZM precipitation rate consists primarily of drizzle (Figure~\ref{fig:4zonal}d). The predominance of drizzle in this region is probably a result of the large subsiding motion in the subtropics (not shown) constraining CAPE from becoming too large. AGCMs are known to suffer from an excess drizzle bias in precisely this region \citep{D2006JCLIM}, and this analysis indicates that this bias is due to the use of a CAPE trigger function.

>>>>

\subsection{Vertical Velocities and the Drizzle Bias}

AGCMs are known to suffer from producing too much light rain, or drizzle, relative to observations, predominantly in the subtropics \citep{D2006JCLIM}. Figure~\ref{fig:4zonal}d shows the fraction of ZM precipitation that is less $\leq 5$ mm/day in the simulations, which stubbornly persists at 70\% of ZM precipitation in the region between $10^{\circ}-20^{\circ}$ latitude at all resolutions. In this region, there are opposing influences on dilute CAPE, a global maximum in latent heat fluxes (Figure~\ref{fig:4zonal}c) which increases dilute CAPE from below, and abundant subsidence, opposing dilute CAPE from above.

%Poleward of the deep tropics and within the subtropics, the logistic regression indicates that subsidence is a poor predictor of $FREQZM$ (Figure~\ref{fig:4zonal}a,b). The R-value decreases to a local minimum between $15^{\circ} - 20^{\circ}$ latitude, and the magnitude of the sensitivity parameter steeply declines. The local minimum in the R-value corresponds with a local maximum in the latent heat fluxes (Figure~\ref{fig:4zonal}c), indicating that the boundary layer is being driven unstable by large surface latent heat fluxes. The CAPE values in the $10^{\circ} - 15^{\circ}$ latitude region are likely to be small, since the ZM precipitation rate consists primarily of drizzle (Figure~\ref{fig:4zonal}d). The predominance of drizzle in this region is probably a result of the large subsiding motion in the subtropics (not shown) constraining CAPE from becoming too large. AGCMs are known to suffer from an excess drizzle bias in precisely this region \citep{D2006JCLIM}, and this analysis indicates that this bias is due to the use of a CAPE trigger function.
